Results_setup

### 2020-06-23 src/Result_Setup.Rmd
finalizing the v3 draft

                       # Nmice = length(Nmice, na.rm = TRUE),
                        Ncells  = sum(Ncells, na.rm = TRUE), #might not to be sum
                        mean.SC = mean(mean_SC, na.rm =TRUE),
                        var.SC = mean(var, na.rm = TRUE), #mouse average variance of bivalent per mouse
                        #chrm classes
                        av.proportion_0CO = mean(proportion_0CO, na.rm = TRUE),
                        av.proportion_1CO = mean(proportion_1CO, na.rm = TRUE),
                        av.proportion_2CO = mean(proportion_2CO, na.rm = TRUE),
                        av.proportion_3CO = mean(proportion_3CO, na.rm = TRUE),
                        #1CO pos
                        mean.1CO.pos = mean(mean_1CO.pos, na.rm = TRUE),

@@

```{r Female.specific.glm.M4.M5, echo=FALSE, eval=TRUE}

@@

```{r Male.specific.glm.M4.M5, echo=FALSE, eval=TRUE}
#M4
MLH1.male.glm.M4 <- glm(mean_co ~ subsp * strain, data=(male_mouse.avs_for.analysis  %>% filter(subsp != "Cast") )   )

@@

@@

Q2tot.sc_t.test_High.Low <- t.test( (mouse.total.skel %>% filter(sex == "male") %>% filter(Rec.group == "0") %>% filter(species == "M.musculus") )$mean.skel,
                (mouse.total.skel %>% filter(species == "M.musculus") %>% filter(sex == "male") %>% filter(Rec.group == "1") )$mean.skel)

#mol -- why is there only 1 MOLF male now?
#there are 3 MOLF males in bivdata
Q2tot.sc_t.test_High.Low_Mol <- t.test( (mouse.total.skel %>% filter(sex == "male") %>% filter(Rec.group == "0") %>% filter(subsp == "Mol") )$mean.skel,
         (mouse.total.skel %>% filter(sex == "male") %>% filter(Rec.group == "1") %>% filter(subsp == "Mol") )$mean.skel)

@@

The molf male t-tests don't work because I only have total Sc measures for 1 MOLF male.

@@

Q2short.biv_t.test_High.Low <- t.test((Q2mouse.av.short.biv.table %>% filter(Rec.group == "0") )$mean.SC,
                                      (Q2mouse.av.short.biv.table %>% filter(Rec.group == "1") )$mean.SC)

@@

```{r Q2.SC_across.subsp_short.long.mus.av, echo=FALSE, eval=FALSE}

#DOM-musc-long
Q2.long_t.test_DomMusc <- t.test((Q2mouse.av.long.biv.table  %>% filter(subsp == "Dom") )$mean.SC,
                          (Q2mouse.av.long.biv.table %>% filter(subsp == "Musc"))$mean.SC)
#p-value = 0.08

#DOM-musc-short
Q2.short_t.test_DomMusc <- t.test((Q2mouse.av.short.biv.table  %>% filter(subsp == "Dom") )$mean.SC,
                          (Q2mouse.av.short.biv.table %>% filter(subsp == "Musc"))$mean.SC)
#p-value = 0.8

#DOM-mol-long
Q2.long_t.test_DomMol <- t.test((Q2mouse.av.long.biv.table  %>% filter(subsp == "Dom") )$mean.SC,
                          (Q2mouse.av.long.biv.table %>% filter(subsp == "Mol"))$mean.SC)
#p-value = 0.4

#DOM-mol-short
Q2.short_t.test_DomMol <- t.test((Q2mouse.av.short.biv.table  %>% filter(subsp == "Dom") )$mean.SC,
                          (Q2mouse.av.short.biv.table %>% filter(subsp == "Mol"))$mean.SC)
#p-value = 0.09

@@

```{r Female.specific.glm.M4.M5-temp, echo=FALSE, eval=TRUE}
#Change MLH1 to mean_skel

@@

```{r Q2.glm.SC.long, echo=FALSE, eval=FALSE}

#this dataset is all males
glmQ2_long.biv_M4 <- glm(mean.SC ~ subsp * strain, data= Q2mouse.av.long.biv.table)
sum.glmQ2_long.biv_M4 <- summary(glmQ2_long.biv_M4)

glmQ2_long.biv_M4 <- glm(mean.SC ~ strain, data= Q2mouse.av.long.biv.table)
sum.glmQ2_long.biv_M4 <- summary(glmQ2_long.biv_M4)
#round(sum.glmQ2_long.biv_M2$coefficients[,c(1,4)], 6)

glmQ2_long.biv_M4.2_DOM <- glm(mean.SC ~ strain, data= ( Q2mouse.av.long.biv.table %>% filter(subsp == "Dom") )  )
sum.glmQ2_long.biv_M4.2_DOM <- summary(glmQ2_long.biv_M4.2_DOM)

#MUSC
glmQ2_long.biv_M4.2_MUSC <- glm(mean.SC ~ strain, data= ( Q2mouse.av.long.biv.table %>% filter(subsp == "Musc") )  )
sum.glmQ2_long.biv_M4.2_MUSC <- summary(glmQ2_long.biv_M4.2_MUSC)

#MOL can't be done -- only 1 mouse for each MSM and MOLF
glmQ2_long.biv_M4.2_MOL <- glm(mean.SC ~ strain, data= ( Q2mouse.av.long.biv.table %>% filter(subsp == "Mol") )  )
sum.glmQ2_long.biv_M4.2_MOL <- summary(glmQ2_long.biv_M4.2_MOL)

#pairwise.t.test( ( Q2mouse.av.long.biv.table %>% filter(subsp == "Musc") )$mean.SC, ( Q2mouse.av.long.biv.table %>% filter(subsp == "Musc") )$strain )

>>>>

                       # Nmice = length(Nmice, na.rm = TRUE),
                        Ncells  = sum(Ncells, na.rm = TRUE), #might not to be sum
                        mean.SC = mean(mean_SC, na.rm =TRUE),
                        var.SC = mean(var, na.rm = TRUE), #mouse average variance of bivalent per mouse
                        #chrm classes
                        av.proportion_0CO = mean(proportion_0CO, na.rm = TRUE),
                        av.proportion_1CO = mean(proportion_1CO, na.rm = TRUE),
                        av.proportion_2CO = mean(proportion_2CO, na.rm = TRUE),
                        av.proportion_3CO = mean(proportion_3CO, na.rm = TRUE),

                        #1CO pos
                        mean.1CO.pos = mean(mean_1CO.pos, na.rm = TRUE),

@@

```{r MLH1.Female.specific.glm.M4.M5, echo=FALSE, eval=TRUE}

@@

```{r MLH1.Male.specific.glm.M4.M5, echo=FALSE, eval=TRUE}
#M4
MLH1.male.glm.M4 <- glm(mean_co ~ subsp * strain, data=(male_mouse.avs_for.analysis  %>% filter(subsp != "Cast") )   )

@@

#rerun as strain means
Q1.strain.F1.Pos <- t.test(
( strain.BivData.Table %>% filter(species == "M.musculus") %>% filter(sex == "male") %>% filter(strain != "CZECH") %>% filter(strain != "MOLF") )$mean.1CO.pos,

  ( strain.BivData.Table %>% filter(species == "M.musculus") %>% filter(sex == "female"))$mean.1CO.pos, paired = TRUE  )

@@

Q2tot.sc_t.test_High.Low <- t.test( (mouse.total.skel %>% filter(sex == "male") %>% filter(Rec.group == "0") %>% filter(species == "M.musculus") %>% filter(subsp != "Cast") )$mean.skel,
                (mouse.total.skel %>% filter(species == "M.musculus") %>% filter(sex == "male") %>% filter(Rec.group == "1") )$mean.skel)

Q2tot.sc_t.test_High.Low_Mol <- t.test( (mouse.total.skel %>% filter(sex == "male") %>% filter(Rec.group == "0") %>% filter(subsp == "Mol") )$mean.skel,
         (mouse.total.skel %>% filter(sex == "male") %>% filter(Rec.group == "1") %>% filter(subsp == "Mol") )$mean.skel )

@@

@@

Q2short.biv_t.test_High.Low <- t.test((Q2mouse.av.short.biv.table %>% filter(Rec.group == "0") %>% filter(subsp != "Cast") )$mean.SC,
                                      (Q2mouse.av.short.biv.table %>% filter(Rec.group == "1") )$mean.SC)

@@

@@

```{r Female.specific.glm.M4.M5, echo=FALSE, eval=TRUE}
#Change MLH1 to mean_skel

@@

```{r Q2.glm.SC.long, echo=FALSE}
Q2mouse.av.long.biv.table$strain <- factor(Q2mouse.av.long.biv.table$strain, ordered = F)
Q2mouse.av.long.biv.table$subsp <- factor(Q2mouse.av.long.biv.table$subsp, ordered = F)

#this dataset is all males
male.Long_M4 <- glm(mean.SC ~ subsp * strain, data= Q2mouse.av.long.biv.table)
sum.male.Long_M4 <- summary(male.Long_M4)

write.xlsx(as.data.frame( sum.male.Long_M4$coefficients), "male.long.M4.xlsx", col.names = TRUE, row.names = TRUE)

#Q2mouse.av.long.biv.table$um.SC <- add_umeter(Q2mouse.av.long.biv.table$mean.SC)

male.Long_M5 <- glm(mean.SC ~ strain, data= Q2mouse.av.long.biv.table)
sum.male.Long_M5 <- summary(male.Long_M5)

write.xlsx(as.data.frame( sum.male.Long_M5$coefficients), "male.Long_M5.xlsx", col.names = TRUE, row.names = TRUE)
